### 2018-04-19 Manuscript/chapter4.tex
Add results

Samples were sequenced starting on January 14, 2016 at the Iowa State University DNA Facility (Platform: Illumina HiSeq Sequencing; Category: Single End 100 cycle sequencing). A standard Illumina mRNA library was prepared by the DNA facility. Reads were aligned to the BeeBase Version 3.2 genome (\citealt{hbGenome}) from the Hymenoptera Genome Database (\citealt{hymenopteraDB}) using the programs GMAP and GSNAP (\citealt{gsnap}). We tested all six pairwise combinations of treatments for DEGs (pairwise DEGs). We also tested the diet main effect (diet DEGs), virus main effect (virus DEGs), and interaction term for DEGs (interaction DEGs). We then also tested for virus main effect DEGs (virus DEGs) in public data derived from a previous study exploring the gene expression of IAPV virus infection in honeybees (\citealt{galbraith}). We tested each DEG analysis using recommended parameters with DESeq2 (\citealt{deseq2}), edgeR (\citealt{edger}), and LimmaVoom (\citealt{limma}). In all cases, we used a false discovery rate (FDR) threshold of 0.05 (\citealt{benjamini}). Fisher's exact test was used to determine significant overlaps between DEG sets (whether from the same dataset but across different analysis pipelines or from different datasets across the same analysis pipelines). The \pkg{eulerr} shiny application was used to construct Venn diagram overlap images (\citealt{euler}).

@@

DEGs were uploaded as a background list to DAVID Bioinformatics Resources 6.7 (\citealt{davidBio}, \citealt{davidBio2}). The overrepresented gene ontology (GO) terms of DEGs were identified using the BEEBASE\_ID identifier. To fine-tune the GO term list, only significant terms (FDR < 0.05) and those correlating to Biological Processes were considered. The refined GO term list was then imported into REVIGO (\citealt{revigo}), which uses semantic similarity measures to cluster long lists of GO terms.

@@

@@

% SYNTAX
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\ref{sec:ggenealogy}
% \code{ggparcoord}
% \Figure \ref{fig:porcupine}

% \begin{figure}[H]
% \centering
%     \begin{framed}
%     \includegraphics[width=0.8\textwidth]{porcupine}
%     \end{framed}
%     \caption{Three}
%     \label{fig:porcupine}
% \end{figure}

% \section{Literature review}
% \label{sec:litReview}

% \pkg{R} statistical programming language allows for tools to be distributed and modified at ease, encourages cross-platform collaboration, and provides a foundation for effective and aesthetic data visualization from the grammar of graphics. There are several useful \pkg{R} packages that offer tools for analyzing and visualizing genealogical datasets. Here, we introduce these packages, and emphasize the shortcomings for which our package \pkg{ggenealogy} brings to this collection of work.

%\clearpage

%\begin{enumerate}
%\item The data can be viewed at \url{http://shiny.soybase.org/CNV/}.
%\end{enumerate}

@@

>>>>

Samples were sequenced starting on January 14, 2016 at the Iowa State University DNA Facility (Platform: Illumina HiSeq Sequencing; Category: Single End 100 cycle sequencing). A standard Illumina mRNA library was prepared by the DNA facility. Reads were aligned to the BeeBase Version 3.2 genome (\citealt{hbGenome}) from the Hymenoptera Genome Database (\citealt{hymenopteraDB}) using the programs GMAP and GSNAP (\citealt{gsnap}). We tested all six pairwise combinations of treatments for DEGs (pairwise DEGs). We also tested the diet main effect (diet DEGs), virus main effect (virus DEGs), and interaction term for DEGs (interaction DEGs). We then also tested for virus main effect DEGs (virus DEGs) in public data derived from a previous study exploring the gene expression of IAPV virus infection in honeybees (\citealt{galbraith}). We tested each DEG analysis using recommended parameters with DESeq2 (\citealt{deseq2}), edgeR (\citealt{edger}), and LimmaVoom (\citealt{limma}). In all cases, we used a false discovery rate (FDR) threshold of 0.05 (\citealt{benjamini}). Fisher's exact test was used to determine significant overlaps between DEG sets (whether from the same dataset but across different analysis pipelines or from different datasets across the same analysis pipelines). The \pkg{eulerr} shiny application was used to construct Venn diagram overlap images (\citealt{euler}). In the main section of our paper and in subsequent analyses, we focus on the DEG results from DESeq2 (\citealt{deseq2}) as this pipeline was also used in the Galbraith study (\citealt{galbraith}).

@@

DEGs were uploaded as a background list to DAVID Bioinformatics Resources 6.7 (\citealt{davidBio}, \citealt{davidBio2}). The overrepresented gene ontology (GO) terms of DEGs were identified using the BEEBASE\_ID identifier. To fine-tune the GO term list, only significant terms (FDR < 0.05) and those correlating to Biological Processes were considered. The refined GO term list was then imported into REVIGO (\citealt{revigo}), which uses semantic similarity measures to cluster long lists of GO terms. @@@ Pathways analysis @@@

@@

\subsection{Main effect results}

We observed a substantially larger number of DEGs in our diet main effect (n = 1914) than in our virus main effect (n = 43) (Table \ref{tbl:mainEffectDEGs}A and B). In the diet factor, there were more Castanea DEGs (n = 1033) than Rockrose DEGs (n = 881). In the virus factor, there were more virus-exposed DEGs (n = 38) than control DEGs (n = 5). While these reported DEGs numbers are from the DESeq2 package, we saw similar trends for the edgeR and limma package results (Table \ref{tbl:mainEffectDEGs}A and B). Pathway

@@

@@

\section{Appendix}

% \begin{table}
%   \caption{A stunning table}
%   \label{tbl:excel-table}
%   \includegraphics[width=\linewidth]{excel-table}
% \end{table}

\begin{table}[H]
  \includegraphics[width=0.65\textwidth]{Images/mainEffectDEGs}
  \caption{Number of DEGs across three analysis pipelines for (A) the diet effect in our study, (B) the virus main effect in our study, and (C) the virus main effect in the Galbraith study.}
  \label{tbl:mainEffectDEGs}
\end{table}
